% “Everything must be made as simple as possible. But not simpler.” 
\section*{Summary} 
I am young and ambitious. I am interested in solving challenging
problems. I am very keen on algorithms and physics. I have 7+ years of
experience working with C++, strong background in computer
science, math and physics, solid knowledge of algorithms and
data structures, experience with the design and implementation
of complex algorithms. I am able to learn new subjects quickly and
thoroughly.
%Any fool can know. The point is to understand.
% “The only thing that interferes with my learning is my education.” 
%  “The more I learn, the more I realize how much I don't know.” 
\section*{Education}
\mydegree{2011--2013}
{Simulation Sciences - Master of Science}
{RWTH Aachen University, Germany}

\mydegree{2006--2010}
{Physics - Bachelor of Science}
{Sofia University, Bulgaria}

\mydegree{1999--2006}
{High School Degree}
{Math School Pleven, Bulgaria\\ &Top of Graduates}
% “Genius is 1% talent and 99% percent hard work...” 
% The only source of knowledge is experience. 
% Learning is experience. Everything else is just information.
\section*{Experience}
\myjob{2014--present}
{Software Developer}
{Chaos Group, Sofia, Bulgaria}
{Involved in Development and maintenance of raytracer V-Ray and fluid simulator PhoenixFD, formation of company public image and mentoring interns.}
{Integrated Embree library in V-Ray core, which resulted on average in 10\% better render times. Solved some precision problems in both Embree and V-Ray. Optimized V-Ray hair shading and improved Embree hair intersection model.}
{Gained experience of cross platform software development, working in large team, code reviews, git, cmake, sse intrinsics.}
\myjob{2013--2014}
{Algorithm Developer}
{RWTH Aachen}
{Implement scalable parallel singular value decomposition with multiple relatively robust representations}
{Gained knowledge in numerical stability of algorithms}
{Gained experience of multithreaded programing, unit testing, git}

