\myjobb{2012--2013}
{Student Research Assistant} 
{Process Engineering Department, RWTH}
{Aachen, Germany}
{ \item Researched image processing algorithm to collect valuable experimental data}
{ 
%\item Provided valuable insight to project
\item Developed proof of concept algorithm and developed simulator to validate it}
{C++, computer graphics, linear algebra, sparse matrices, raytracing, mathematical optimization}
\myjobb{2011--2012}
{Student Research Assistant}
{Parallel Programing Lab, RWTH}
{Aachen, Germany}
{\item Simulations on Blue Gene/Q}
{\item Developed a tool to process data}
{ C++, MPI, bash, xml, parsing}
\myjobbb{2010--2011}
{Algorithm developer}
{MM Solutions}
{Sofia, Bulgaria}
{ \item Developed algorithms for digital video stabilization project}
{C++, digital image processing, pattern recognition, statistics beyond the university level, testing}
\myjobbb{Summer 2008}{Software Consultant}
{Scopic Software, Rutland MA, USA}{Sofia, Bulgaria}
{\item Maintained Image Processing Software}
{C\#, digital image processing, pattern recognition, classification algorithms, workflow with quality assurance}

\myjobb{2006--2010}{Student Research Assistant}
{Dosimetry and Rad. Protection, Sofia University} {Sofia, Bulgaria}
{
 \item Involved in scientific projects 
 \item Co-author of 9 papers
 \item Developed software for automation of experiments
}
{ 
 \item Developed Monte Carlo for Positron Emission Tomography
 \item Gathered, analysed and visualized data from supercomputers
}
{Linux, C/C++, Pascal, Fortran, OOP, Design Patterns, Monte Carlo, Revision control, High Performance Computing and many more}
\vspace{-0.8cm}
\mysection{Personality Strengths}
\small
\textbf{Knowledgeable} - I rarely pass up a good opportunity to learn something
new. I just find it fun and fascinating.\\
\textbf{Original and Energetic} - If presented with chronic, systemic
problems, I respond with enthusiasm and energy, putting days and nights to find a solution.\\
\textbf{Critical Thinker} - In quest for best solutions, I enjoy to analyze problems from every angle. I easily use my accumulated knowledge to identify fallacious arguments and systematical contradictions. Therefore, I can produce factual knowledge that can be trusted.\\
\textbf{Excellent Brainstormer} - I am confident in my abilities. I
have passion to share my opinion, knowledge and critical thinking with my colleagues.\\
\textbf{Charismatic} – People find intriguing my way with words. My confidence, quick thought and ability to connect distant ideas in novel ways create a style of communication that is charming, entertaining, and informative at the same time.\\
\textbf{People Master} - I have very good communication skills, feeling at ease in social events or in situations where I need to connect to other people. Playing an active role in the society and knowing what makes other people tick means a lot for me. However, I am not influenced easily by others opinion about me.


